CS378: Final Project - Data Artifacts \\ \url{https://github.com/sarimaleem/cs378_fp}

### 2023-04-27 paper/main.tex
progress

\documentclass[twocolumn]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tabularx,ragged2e,booktabs,caption}
\usepackage{multirow}
\usepackage{color}
\usepackage[top=1in,bottom=1in,left=1.2in,right=1.2in]{geometry}
\usepackage{hyperref}
\usepackage[small]{titlesec}
\usepackage{cite}

@@

\todo{You should describe modifications you have made to improve performances.
We will evaluate based on how reasonable is your fix  -- if your fix and
motivation does not link, your modificiation is unreasonable. For example,
perhaps you tried to modify neural network training in a way that is totally
unconnected to your stated goal, or your modification was erroneous. Describe
the baseline model to be compared to your approach as well here. Again, clearly
define all notations. Someone who is reading your report (with reasonable
background, e.g., your classmates in this course) should have a reasonable idea
how to implement it themselves. Describe hyperparameters, including how they
are selected, if you have hyperparameters involved. }

>>>>

\documentclass[twocolumn]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tabularx,ragged2e,booktabs,caption}
\usepackage{multirow}
\usepackage{color}
\usepackage[top=1in,bottom=1in,left=1.2in,right=1.2in]{geometry}
\usepackage{hyperref}
\usepackage[small]{titlesec}
\usepackage{cite}
\usepackage{graphicx}

@@

It is clear that the issue with the model is that it fails to understand
ambiguous training examples. This is especially seen given that the model
largely confuses, as seen earlier, neutral and entailment and instances of
contradiction.

\begin{figure}
  \includegraphics[width=\linewidth]{./ambiguous.jpg}
  \caption{Data Cartogram of 2000 training examples}
  \label{}
\end{figure}

\subsection{Dataset Cartography}

Training on labels that are ambiguous, that have high variablity, should in
theory help with this issue, even more so than hard to learn labels. An
ambiguous label is defined as a label that has high variance when predicted by
different iterations of the model. For example, a model that is trained on 500
iterations would predict the input differently than a model trained with 1000
iterations or a model trained with 1500 iterations. Furthermore, the average
confidence of that training example is not high or low.
\cite{swayamdipta2020dataset} We reproduced the code to analyze data, and have
plotted 500 training examples in figure 1.

In order to deal with this, we first created a program that finds ambiguous
examples. We found the variance of the training example based on its confidence
of the gold label from a modeled trained on 500 iterations, 1000 iterations,
1500 iterations, 2000 iterations, 2500 iterations, and 3000 iterations. If th
variance was greater than 0.2, and the confidence of the model was in between
0.6 and 0.7, the example was deemed ambiguous. According to \textit{Swayamdipta
et al.}, training solely ambiguous examples leads to to greater performance
than training on the whole dataset, only easy to learn examples, or only hard to
learn examples. Thus it is logical to train on these examples.

We pulled 1655 ambiguous samples from the training data and trained on those examples.
